\documentclass[12pt]{article}
% copy this template file to weekxx.tex, e.g.m for week 1, week01.tex
% and edit the new file.

\usepackage{amssymb,amsthm,amsmath,amsfonts}
\usepackage{fullpage}
\usepackage{todonotes}

\usepackage[parfill]{parskip}

\title{Computational Plasma Physics}
\author{Dhruv}
\date{\today}

\begin{document}
\maketitle

\subsubsection*{Pre--Meeting Logbook}
\begin{enumerate}
\item What were the objectives for this week?

  \begin{itemize}
  \item (Copy from previous notebook)
  \end{itemize}

\item What were (are) the difficulties/obstacles you faced (are
  facing)?

  \begin{itemize}
  \item
  \end{itemize}


\item How would you quantify your progress (in terms of a percentage)?

  \begin{itemize}
  \item {\em  xx \%}
  \end{itemize}

\item What questions developed this week?

    \begin{itemize}
    \item
    \end{itemize}

\item What do you anticipate working on by friday?

  \begin{itemize}
  \item (ideal: 30 min) compiling example using math library for
    linear solve in C
  \item (ideal: 30 min) finish complete PIC 1D, using linear solve,
    math library in C.
  \item (ideal: 1 hour) learn lexographical ordering for solving for
    potential on grid in 2D
  \item (ideal 2 hours) generate coefficient matrix and solve for
    potential in 2d (matlab)
  \item (ideal 2 hours) finish reading treecode paper.  come armed
    with questions or summary.
  \item (ideal 3 hours) start summary of treecode in overleaf report
  \item (ideal 1 hours) knock of at least one todo in the overleaf
    report.
  \item start treecode in matlab, 1D
    \begin{itemize}
    \item (15 minutes) initalization of simulation.  one single
      particle at location (0,0), ten particles clustered around
      location (1,0).
    \item (1 hour): write function that takes derivatives of
      regularized potential
      \begin{align*}
        G^\epsilon = \frac{1}2{}\sqrt{(x-x_j)^2 + \epsilon^2}
      \end{align*}
    \item (10 minutes): 0th order treecode approx, assuming all
      particles clustered around (1,0) are a cluster.
    \item (2 hours): 1st order treecode approx, assuming all
      particles clustered around (1,0) are a cluster.
    \item (30 minutes): 2nd order treecode approx, assuming all
      particles clustered around (1,0) are a cluster.
    \end{itemize}
  \item if you have time: start generating coefficient matrix for C
  \end{itemize}


\end{enumerate}

\subsubsection*{Post--Meeting Logbook}
\begin{enumerate}
\item Recap of today's research meeting

  \begin{itemize}
  \item
  \end{itemize}

\item What will you work on this coming week?

  \begin{itemize}
  \item
  \end{itemize}


\end{enumerate}

\end{document}
